\begin{rubric}{Employment and internships}
%
% Blank lines result in extra space!
%
\subrubric{After PhD}
\entry*[Sep 2020 -- \textit{Aug 2023}]%
\textbf{Postdoctoral researcher} \par
\textbf{Company} Wellcome Sanger, Cambridge, United Kingdom \par
\textbf{keywords} Single cell RNA-seq, VDJ, and CITE-seq; eQTLs; Lupus; immune traits

\subrubric{After M.Sc.}
\entry*[Mar 2015 -- May 2015]%
\textbf{Assistant Webmining} \par
\textbf{Company} TextKernel, Amsterdam, Netherlands

\subrubric{During M.Sc.}
\entry*[Jan -- Jun 2014]%
\textbf{Connecting multiple gene expression signatures with candidate drugs for boosting heart regeneration potential.} \par
\textbf{Supervisor} Dr. Francisco Azuaje \par
\textbf{Institute} CRD-Sante\'e, Luxembourg, Luxembourg \par
\textbf{Grade} 9/10 \par
\url{https://github.com/npklein/drugFinder}
%Identified novel drug candidates which can boost the heart regeneration of zebrafish using microarray expression data.
%
\entry*[Aug -- Dec 2013]%
\textbf{Clustering of MS/MS spectra to improve peptide and protein identification.} \par
\textbf{Supervisor} Dr. Tham Pham \par
\textbf{Institute} Cancer Center Amsterdam, Amsterdam, Netherlands\par
\textbf{Grade} 9/10 \par
%Clustered unidentified spectra from mass spectrometer measurements together with identified spectra to improve peptide and protein identification.
%
\entry*[Dec 2012 -- Aug 2013]%
\textbf{Assistant Webmining} \par
\textbf{Company} TextKernel, Amsterdam, Netherlands

%


\subrubric{During B.Sc.}
\entry*[Feb -- Jun 2012]%
\textbf{Methods to assess the reproducibility and coverage of tandem mass spectrometry data in phosphoproteomics experiments.} \par
\textbf{Supervisor} Dr. David Martin \par
\textbf{Institute} Wellcome Trust, Dundee, Scotland \par
\textbf{Grade} 9/10 \par
%Developed a Python module to perform statistical analysis on mass spectrometry data.\par
\url{https://github.com/npklein/pyMSA}
%
\entry*[Oct 2011 -- Oct 2012]%
\textbf{Junior Developer} \par
\textbf{Company} iVention, Amesfoort, Netherlands
%
\entry*[Sep -- Dec 2010]%
\textbf{How widespread are microProteins and how did they evolve?} \par
\textbf{Supervisor} Dr. Sue Rhee \par
\textbf{Institute} Carnegie Institue for Life Sciences, Stanford, USA \par
\textbf{Grade} 8/10 \par
%Wrote a program in Python to identify putative microProteins. \par
\url{https://github.com/npklein/miP3}


\end{rubric}