%!TEX encoding = UTF8
%!TEX root =cv-llt.tex


\begin{rubric}{Skills}
\entry*[]
\circled{} refer to publications, see Research Publications section. 
\subrubric{Genomics/Genetics}
\entry*[Single cell]
	Experience with computational analysis of single cell RNA-seq, CITE-seq, and vdj-seq.
\entry*[QTLs]
	Experience with downstream analysis of eQTLs (\circled{2},  \circled{9}, \circled{12}) as well as developing new software for calculating interaction eQTLs ( \circled{8} and github.com/npklein/systemsgenetics/tree/master/Decon2 )
\entry*[Differential expression]
	Experience running differential expression analysis (\circled{10}).
\entry*[(G/E)WAS]
	Experience running EWAS as part of large consortium (\circled{4}, \circled{5}). 
\entry*[Method development]
	Experience developing new methods for gene identification (\circled{17} and \circled{18}), gene ID mapping between species (\circled{16}), improving protein identification from mass spectrometry (See B.Sc. and M.sc. internships), and identifying cell type specific eQTL effects in bulk data (\circled{8}).
\subrubric{Coding}
\entry*[Coding]
Most experienced in R Bash, Python. Experience in Java. Code on \url{github.com/npklein}. Code written during current employment is in a private repository, can share recent examples on request. 
\entry*[Databases]
	Experience with My\smallcaps{SQL} and \smallcaps{SQL}ite
\subrubric{General}
\entry*[Writing]
Experience writing scientific articles (See Research Publications below).
\entry*[Teaching and supervision]
Experience giving workshops and lectures (See Teaching below). Experience supervising students (See Teaching below for details.)
\entry*[Presenting work]
Regular presentations at group and departmental level. Presenting monthly for stakeholders from industry on project progress as part of OpenTargets private-public collaboration.
\entry*[Languages]
Strong reading, writing and speaking competencies for English and Dutch (native).

\end{rubric}